A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-08-26 main.tex
Final figure updates

\anna{REPLACE FIGURES WITH RESULTS FROM PLMM-LASSO ONCE FINISHED}

@@

Conversely, in settings where $n \ge p$, LMM-Lasso-ggmix is up to 10 times faster than LMM-Lasso-Rakitsch. However, these are also settings in which LMM-Lasso Rakitsch outperforms LMM-Lasso-ggmix in estimating $\bbeta$ and $\eta$ accurately and consistently, likely due to the ill-conditioning of the RRM \anna{cite French paper (?)}.

@@

\anna{add some info/figure on convergence and number of iterations for lmm-lasso vs ggmix}

>>>>

@@

Conversely, in settings where $n \ge p$, LMM-Lasso-ggmix is up to 10 times faster than LMM-Lasso-Rakitsch. However, these are also settings in which LMM-Lasso Rakitsch outperforms LMM-Lasso-ggmix in estimating $\bbeta$ and $\eta$ accurately and consistently, likely due to the ill-conditioned RRM \citep{ledoit2004well}.

@@
